How much gut content data is required to predict trophic interactions?

### 2022-02-28 manuscript/ms_C2/ms_C2.Rmd
Very minor
Update ms_C2.Rmd

---
title: Optimal amount of gut content data required to predict trophic interactions using a food web model
authors:
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: anubhav.gupta@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Anubhav Gupta
  thanks: Corresponding author
- affiliation: University of Essex
  department: School of Life Sciences
  email: e.ogorman@essex.ac.uk
  location: CO4 3SQ Colchester, UK
  name: Eoin O' Gorman
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: owen.petchey@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Owen L. Petchey
geometry: margin=1in
abstract: |

  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as allometric diet  breadth model (ADBM), thereby predicting interactions. And collecting and analysing these data from the field is an expensive and time consuming task. Therefore, it is crucial to know how much gut content data is required to parameterise the ADBM with high accuracy and high precision for a given food web with minimum sampling effort.
  2)  The novelty of our current approach is that we use approximate Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit for different amount of predators' gut content data. 
  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM for total gut content data. We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the total gut content data.
  4)  These results suggest that one need not collect a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably.

@@

Although food web models are constructed using prior theory about the factors that determine trophic interactions, empirical data about interactions is required to parameterise a model. For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions. These empirical information about interactions can be inferred from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].

@@

Food web methods mentioned above have multiple shortcomings. Stable isotope ratio analysis of the organism's tissue does not give a direct information of the diet of that organism but rather approximate trophic position of that species in the food web. Although mixing models can be used to determine what prey items are most likely fed upon by a predator but this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008]. Experimentation (e.g. feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd). DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e. the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator's gut. Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g. from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993]. This typically results in a food web that will be very oversampled with false positives in the presence of links (citreqd). @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods. \*\*AG: Working on this paragraph.

Acquiring food web data from gut content analysis is time consuming and expensive (reference). In part this is due to the need for many gut contents to be collected and analysed in order to be confident that the majority of possible trophic links have been observed. Furthermore, considerable time, resource investment, and expertise is required to process the collected samples. Hence, there is of considerable importance to know the minimum number of gut contents and of which consumer species that are required to parameterise a food web model with high accuracy and high precision, so that one knows when is a good time to stop collecting any further empirical data on the food web.

Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model specifically the ADBM with high accuracy and high precision. In other words, how many samples of gut content should one collect from the field to parameterise a food web model? To answer this question, we use the presence-absence information from gut content data to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, where the fitness of the model was measured using true skill statistics. We computed the true skill statistics of the predicted food webs for different number of predator guts to calculate the minimum number of gut content data to infer food web structure. Our study provides a guideline on how many gut content data is required to predict food web structure using a food web model.

@@

In the upcoming sections, we present the food webs, the allometric diet breadth model (ADBM) and the gut content data used to infer the trophic interactions in the presented food webs using the ADBM. We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC). We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.

@@

In our study, we used food webs for which gut content data is available at an individual level and, is FAIR. Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011]. A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g. species) and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former. Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes. Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.

@@

Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web. However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010]. This could result in a lower TSS of the predicted food web from the ADBM which can result in a biased estimate of the number of gut content data.

@@

@@

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966]. We chose this model because it uses the body size of organisms as input to predict feeding interactions. The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008]. The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species. Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.

@@

The accuracy of the predicted diet of the predators was defined using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:

$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives.

The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].

@@

From an empirical dataset of gut content data, we draw a set of gut contents data randomly to create a partial gut content dataset. We then fit the ADBM to this partial dataset.

To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic. The true skill statistic was computed between the predators' diet predicted from the ADBM, and that from the sampled gut content data. We repeated this process for $n~(= 100)$ number of times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.

@@

-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is a one-dimensional matrix containing ones and zeros.

-   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is a one-dimensional diet matrix of predator $k$ containing ones and zeros.

-   A summary statistic $s(x): s(x) \subseteq model(\theta)$

-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$

-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$

@@

The $TSS$ between observed and predicted food webs for every $i$ number of gut content data drawn from the pool of gut content data.

@@

We first present how the accuracy of the food web model i.e ADBM vary in predicting trophic interactions with increasing amount of gut content data provided to the food web model. Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model. We also compute the goodness of the food web model in predicting structural properties from incomplete gut content data. We did that by computing mean standardised error in food web properties.

@@

The true skill statistics of the food webs predicted by the ADBM using subsets of gut content data improved quickly for lower number of predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). The prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used. Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.

For Broadstone Stream food web, with only 381 number of gut content data which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data by the ADBM (Fig. \ref{fig:fig_ra}(a)). In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data by the ADBM (Fig. \ref{fig:fig_ra}(c)).

For a low number of predator guts, the TSS of the model predicted food web was higher than the TSS of the food web constructed from gut content data only (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)). After a certain increase in the number of predator guts, the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually.

@@

Mean standardised error in structural properties of afon hirnant, broadstone stream, celtic sea and tadnoll brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig. \ref{fig:fig_rab}). In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.

@@

## Dependence of minimum gut content data on number of species, links and connectance

There was a positive trend between number of minimum gut content data and number of species (S) (Fig. \ref{fig:fig_rb} (a)), links (L) (Fig. \ref{fig:fig_rb} (c)), connectance (C) (Fig. \ref{fig:fig_rb} (d)) and number of predator nodes (Fig. \ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig. \ref{fig:fig_rb} (a, c, e). The number of minimum gut content data increases with number of maximum gut content data sampled (Fig. \ref{fig:fig_rb} (b)). There seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig. \ref{fig:fig_rb} (f)), links (L) (Fig. \ref{fig:fig_rb} (g)), connectance (C) (Fig. \ref{fig:fig_rb} (h)).

@@

We have demonstrated how a food web model can be used to predict food web in the availability of incomplete data. At lower amount of gut content data, ADBM is quite better at predicting trophic interactions. We have computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling. This can help us decide how much gut content data to actually collect when we are using a food web model to infer trophic interactions. A future development could be to use this our approach on other food web models, and to also use food web data other than gut content data to parameterise those models.

@@

In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete gut content data because the presence absence information from the gut content data was used to narrow down the possible model parameter values of the ADBM that best explained the predators' diets. Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rule, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions.

@@

We found the minimum number of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently i.e. some food webs are well sampled than others (Fig. \ref{fig:fig_rc}). Since some food webs are more size-structured than others, they are well predicted by the ADBM and therefore might require a lower number of gut content data for model parameterisation. 
\*\*:AG: I would need to add information about the interactions in these food webs.

## Model fills up missing interactions and guide sampling direction

When only few presence absence data is available, model can be used to fill up the missing interactions that has not been observed in the gut content data. Also model's predictions can be used as a guide to sample predator guts that might be significant in the food web.

@@

Due to limitations of the ADBM as to not able to completely explain the interactions in a food webs using the foraging rules based on the body size and also possible undersampling in the observed data because of missing rare links, the ADBM's maximum predicted true skill statistics is always less than one.

The maximum predictive power of a model is constrained by the rules it is based on. In the case of ADBM, that limits the predictive power of the ADBM is that it can only predict diets that are contiguous with respect to the size of prey. I.e. it cannot predict that a predator with consume prey of size 1 and 3, and not prey of size 2. Also, it is important to note that if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS.

@@

@@

In our study, we have implemented the approach to only the ADBM. However, in principle, this approach could be extended to other food web models. A future prospect could be to study how good different food web models' prediction accuracy vary for different amount of gut content data. This can also help in making decision as to which food web model to chose from given set of gut content data.

A future study could be to use our approach of estimating the minimum gut content data for different food web models. An efficient model would be the one that uses minimum available gut content data to predict species interactions with high accuracy and high precision.

@@

@@

A future prospect would be to include other types of food web data along with gut content simultaneously to parameterise the ADBM. For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and gut content data of a different predator simultaneously to parameterise the ADBM. In this case, trophic position would be an additional summary statistics required in the parameterisation method. This is useful when only limited amount of diet information can be extracted by using a single method.

@@

\*\*OP: Working on this.

@@

\*\*OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here.

@@

## Prediction using simulated gut content data from a simulated food web

@@

The true skill statistics (TSS) between the predicted food web and observed food web saturated with an increasing number of distinct predator guts in a sample (Fig. \ref{fig:fig_r0}). The TSS of the predicted food webs estimated using the complete individual gut data had narrower prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data. The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data. Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts suggesting when we have enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.

>>>>

---
title: How much gut content data is required to predict trophic interactions?
authors:
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: anubhav.gupta@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Anubhav Gupta
  thanks: Corresponding author
- affiliation: University of Essex
  department: School of Life Sciences
  email: e.ogorman@essex.ac.uk
  location: CO4 3SQ Colchester, UK
  name: Eoin O' Gorman
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: owen.petchey@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Owen L. Petchey
geometry: margin=1in
abstract: |

  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as the allometric diet  breadth model (ADBM), thereby predicting interactions. Collecting and analysing these data from the field is, however, an expensive and time consuming task. Therefore, it is crucial to know how much gut content data is required to parameterise food web models with high accuracy and high precision.
  2)  We apply to this problem a recently developed approach, namely Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of gut content data is used in the parameterisation. 
  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM when all available gut content data was used. We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the available gut content data.
  4)  These results suggest that one need not collect such a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.

@@

Although food web models are constructed using prior theory about the factors that determine trophic interactions, empirical data about interactions is required to parameterise a model. For example, @petcheySizeForagingFood2008 used presence-absence information about trophic interactions to parameterise the allometric diet breadth model and thereby predict species interactions. These empirical information about interactions can come from diverse set of methods such as gut content analysis [@peralta-maraverStructureDynamicsStability2017], stable isotope ratio analysis of tissues [@laymanCanStableIsotope2007], experimentation [@warrenSpatialTemporalVariation1989], DNA metabarcoding of gut contents or faeces [@roslinUseDNABarcodes2016] and literature research [@grayJoiningDotsAutomated2015; @cohenSoilInvertebratesChemistry2014; @goldwasserConstructionAnalysisLarge1993a].

@@

Each of these sources of information about trophic interactions has shortcomings. Stable isotope ratio analysis of the organism's tissue does gives indirect information of the diet of that organism via revealing approximate trophic position of that species in the food web. Although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008]. Experimentation (e.g. feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd). DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e. the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator gut. Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g. from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993]. This typically results in a food web that has false positives--links included when in reality no link would occur (citreqd). @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods. \*\*AG: Working on this paragraph.

Acquiring food web data from gut content analysis is time consuming and expensive (reference). In part this is due to the perception that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed. Furthermore, considerable time, resource investment, and expertise is required to process the collected samples. Hence, there is of considerable importance to know the minimum number of gut contents and of which consumer species that are required to parameterise a food web model with high accuracy and high precision, so that one knows when is a good time to stop collecting any further empirical data on the food web.

Therefore, the key question we are interested in answering is how much presence-absence information, in the form of gut content data, is required to infer food web structure from a food web model with high accuracy and high precision. In other words, how many samples of gut content should one collect from the field to parameterise a food web model? To answer this question, we use the presence-absence information from gut content data to parameterise the allometric diet breadth model (ADBM) thereby predicting trophic interactions in seven different food webs using rejection approximate Bayesian computation, where the fit of the model was measured using true skill statistics. We computed the true skill statistics of the predicted food webs for different number of predator guts to calculate the minimum number of gut content data to infer food web structure. Our study provides a guideline on how many gut content data is required to predict food web structure using a food web model.

@@

In the upcoming sections, we present the empirical food webs, the allometric diet breadth model (ADBM), and the gut content data used to infer the trophic interactions. We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC). We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.

@@

In our study, we used food webs for which gut content data is available at an individual level and data that is or that we could make FAIR [OP: cite this https://www.go-fair.org/fair-principles/]. Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011]. A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g. species), or life stages of taxa, and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former. Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes. Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.

@@

Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web. However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010]. This could result in a lower true skill statistic (TSS) of the predicted food web from the ADBM, which can result in a biased estimate of the number of gut content data [OP: this is unclear].

@@

[OP: I like these sections and suggest to include them for other food webs also.]

@@

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966]. We chose this model for various reasons, including because it uses the body size of organisms as input to predict feeding interactions, and because of our familiarity with it. The ADBM predicts the set of prey types (e.g. species or sizes classes) a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008]. The foraging variables in the model are: energy content of the resources, handling times of the prey, space clearance rate, and prey densities. These are allometrically scaled to the body sizes of the species. Further details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petcheySizeForagingFood2008.

@@

The accuracy of the predicted diet of the predators was measured using true skill statistic (TSS) which takes into account the true and false predictions of both the presence and absence of links defined as:

$$ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} $$ where $a$ is the number of observed links that are predicted by the model (true positives), $d$ is the number of observed absences of links that are correctly predicted (true negatives), $b$ is the number of false positives, and $c$ is the number of false negatives. The $TSS$ ranges from $-1$ to $1$, where +1 indicates a perfect prediction. A $TSS$ value of zero or less indicates a performance no better than random [@alloucheAssessingAccuracySpecies2006].

@@

From an empirical dataset of gut content data, we take a random sample of gut contents of specific size (see below) to create a partial gut content dataset. We then fit the ADBM to this partial dataset.

To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic. The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled gut content data. We repeated this process $n~(= 100)$ times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.

@@

-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros. [OP: I made some edits here, which I'm not sure if are correct.]

-   A model prediction $model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}$, where $d_{p_k}$ is the predicted diet matrix of predator $k$ containing ones and zeros.

-   A summary statistic $s(x): s(x) \subseteq model(\theta)$ [OP: a short explanation would be good.]

-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$  [OP: a short explanation would be good.]

-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$  [OP: a short explanation would be good.]

@@

The $TSS$ between observed and predicted food webs, and the posterior parameter distributions for every $i$ number of gut content data drawn from the pool of gut content data.

@@

We first present how the accuracy of the food web model in predicting trophic interactions varies with increasing amount of gut content data provided to the food web model. Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model. We also compute how well  the food web model predicts structural properties from incomplete gut content data. by computing mean standardised error in food web properties.

@@

The true skill statistics of the food webs predicted by the ADBM using subsets of gut content data improved quickly for lower number of predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). Furthermore, the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used. Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.

For Broadstone Stream food web, with only 381 gut contents, which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data (Fig. \ref{fig:fig_ra}(a)). In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data (Fig. \ref{fig:fig_ra}(c)).

For a low number of predator guts, the TSS of the model predicted food web was higher than the TSS of the food web constructed from gut content data only (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)). An increase in the number of predator guts did reduce the ratio TSS(Model)/TSS(data) reduced to less than one, and reduced further gradually. This shows that with less data available it is better to use the model, while if more data is available then it is better to use the data itself.

@@

Mean standardised error in structural properties of Afon Hirnant, Broadstone Stream, Celtic Sea and Tadnoll Brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig. \ref{fig:fig_rab}). In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.

@@

## Dependence of the minimum gut content data on number of species, links and connectance

There was a positive trend between minimum gut content data [OP: minimum that could be used in order to ensure 95% of maximum TSS???] and number of species (S) (Fig. \ref{fig:fig_rb} (a)), links (L) (Fig. \ref{fig:fig_rb} (c)), connectance (C) (Fig. \ref{fig:fig_rb} (d)) and number of predator nodes (Fig. \ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig. \ref{fig:fig_rb} (a, c, e). The minimum gut content data increases with number of gut content data sampled (Fig. \ref{fig:fig_rb} (b)). Furthermore, there seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig. \ref{fig:fig_rb} (f)), links (L) (Fig. \ref{fig:fig_rb} (g)), connectance (C) (Fig. \ref{fig:fig_rb} (h)).

@@

We have demonstrated how a food web model can be used to predict food webs reasonably well even when incomplete data about trophic interactions is available. At lower amount of gut content data, predicting with the model is better than using the data itself, while at higher amounts of gut content data, it is better to only use the data. We computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling [OP: reword this sentence, it is unclear.]. This can help inform how much gut content data to actually collect when we are using a food web model to infer trophic interactions. A future development could be to make the same assessment using other food web models, and to also use food web data other than gut content data to parameterise those models.

@@

In all of the seven food webs, the ADBM was able to infer the trophic interactions using incomplete gut content data because the presence absence information from the gut content data was still sufficient to constrain the possible model parameter values of the ADBM that best explained the predators' diets. Although in theory the ADBM can predict trophic interactions using only body sizes of organisms as it is based on set of foraging rule, it still requires some presence absence data to constrain the posterior parameter space thereby making more accurate predictions.

@@

We found the minimum amount of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently, i.e. some food webs are more extensively sampled than others (Fig. \ref{fig:fig_rc}). Furthermore, it is possible that interactions in some of the food webs are are more size-structured than others, and are therefore better predicted by the ADBM and consequently require a lower number of gut content data for model parameterisation.

\*\*:AG: I would need to add information about the interactions in these food webs.

## Model fills up missing interactions and guides sampling direction

When little data about trophic interactions is available, the model can be used to add data about interactions for which data is missing. Furthermore, the model predictions can be used as a guide to sample predator guts that might be significant in the food web [OP: how? I suggest to explain this in more detail.]

@@

The food web model used (the ADBM) cannot explain all the interactions in any observed food web that it has been fit to. The foraging rules it encodes are based on the body size and have particular structure and assumptions; not all of these are met by all observed interactions. For example, the ADBM can only predict diets that are contiguous with respect to the size of prey. I.e. it cannot predict that a predator will consume taxa of size 1 and 3, and not taxa of size 2. Hence, if the observed diets are not contiguous when prey are ordered by their size, the estimation process could lead to a lower value of the TSS.

Furthermore, the observed data may be missing links, e.g. links that rarely occur. Hence the ADBM's maximum predicted true skill statistics is less than one for all food webs it has so far been fit to.

@@

[OP: This one I already shared with you: https://onlinelibrary.wiley.com/doi/10.1111/ele.13966

@@

In our study, we have implemented the approach only with the ADBM. However, in principle, this approach could be extended to other food web models [OP: such as???]. A future prospect could be to study how well different food web models' prediction accuracy varies for different amount of gut content data. This can also help in making decision as to which food web model to chose from given a set of gut content data.

[OP: seems to not add much relative to the previous paragraph.] A future study could be to use our approach of estimating the minimum gut content data for different food web models. An efficient model would be the one that uses minimum available gut content data to predict species interactions with high accuracy and high precision.

[OP: comment if and why one might expect other food web models to show different efficiency.]

@@

[OP: this paragraph / section needs further development]

@@

A future prospect would be to include other types of food web data along with gut content simultaneously to parameterise the ADBM. For example, one could use the approximate trophic position inferred from stable isotope ratio data from a tissue of an individual and gut content data of a different predator simultaneously to parameterise a food web model such as the ADBM. In this case, trophic position would be an additional summary statistic required in the parameterisation method. This combination of different types of data about trophic interactions could be particularly useful when only a limited amount of diet information can be extracted by using a single method.

@@

@@

\*\*OP: It needs to be very clear in the main text, and here, why this is being described. It is currently unclear, not least because the main text does not, I think, refer to the information here. [OP: I'm not sure my comment has been addressed. We should discuss this.] [OP: I don't see this Supplement being referred to anywhere in the main text. I would expect it to be.] [OP: I advise to integrate the content of this supplement into the main article. There is not so much of it, and it is insightful.]

@@

## Prediction using gut content data from a simulated food web

@@

The true skill statistics (TSS) between the predicted food web and simulated observed food web saturated with an increasing number of distinct predator guts in a sample (Fig. \ref{fig:fig_r0}). The TSS of the predicted food webs estimated using the complete individual gut data had narrower prediction intervals resulting in less uncertainty, and higher mean TSS than that using the partial individual gut data. The maximum limit of the prediction interval of TSS estimated using the complete gut data and the partial gut data were almost equal, with the minimum limit of the prediction interval of TSS using partial gut data being lower than that from the complete gut data. Eventually, the gap between the mean TSS using the partial gut data and the complete gut data reduced with an increasing number of distinct predator guts. This suggests that when there is enough predator species' gut data, the achieved TSS was almost constant and hence independent of the amount of gut data.
